\documentclass[a4paper,11pt]{metu}
\usepackage[latin5]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{layout}

% One essential package for including graphics.
\usepackage{graphicx}

% comment-out following for pdf output with pdflatex. creates hyperlinks
% from toc
% page, figure and table references, and citations. Changes colors of
% hyperlinked text, may be not suitable for official printing. See
% hyperref.sty documentation for changing colors.
%\usepackage{hyperref}

% The following is a nice package if you want to include source code
% segments in your thesis. It pretty prints your source for many languages
% see its documentation
%\usepackage{listings}

% The following is a environment definition to show how you can define new
% labeled and referencable environments. In introduction chapter it is
% used. Just comment out this and the environment use in introduction chapter
% in order to see how it works.

%\newcounter{definition}[chapter]
%\makeatletter
%\newenvironment{definition}
%{\stepcounter{definition}
%  \def\@currentlabel{Dfn.~\thechapter.\thedefinition}
% \begin{flushright}\begin{singlespace}
% \begin{minipage}[t]{0.95\linewidth}\hrule\ \\
% \textbf{Definition \thechapter.\thedefinition}\\}
%{\\\hrule\end{minipage}\end{singlespace}\end{flushright}\vspace{1em}}
%\makeatother



\input{preambl}

\begin{document}

\begin{preliminaries}
\maketitle
\makenewapproval
\makeplagiarismpage
\begin{abstract}
I reverently believe that the maker who made us all  makes everything in New
England, but the weather.  I don't know who makes that, but I think it must be
raw apprentices in the weather-clerks factory who experiment and learn how, in
New England, for board and clothes, and then are promoted to make weather for
countries that require a good article, and will take their custom elsewhere
if they don't get it.

You will be given a post of trust and responsibility.
Beware of a dark-haired man with a loud tie.
You will be audited by the Internal Revenue Service.
\end{abstract}

\begin{oz}
Film bir detektifin bir seri cinayet failinin peşine düşmesi ile başlıyor.
Fakat dedektif öykünün daha 20.sında seri cinayetlerin diğer kurbanları
gibi kızıl saçlı orta yaşlı ve gözlüklü olduğu için katil tarafından öldürülüyor ve
öykü kahramansız kalıyor. İkinci öyküde Agatha Cristie romanlarına bir gönderme
yapılmış. Bir intihar olayını araştırmaya başlayan müfettiş Zuarro zekası ver
kurnazlığı sayesinde katili buluyor. İdam cezasına çarptırılan katil öldükten sonra
slında katilin bu kişi olmadığı, ölen kişinin başka bir tanıdığı olduğu anlaşılıyor. Bu
şekilde 3 kişi daha ipe gönderildikten sonra intiharın sözcük anlamından da
anlaşılabileceği gibi cinayet olmadığı anlaşılıyor. Sinema otoriteleri bu öyküde
yönetmenin sinemaseverleri Agatha Cristie tarzı dedektiflerden tik\-sin\-dir\-me\-yi
amaçladığını ileri sürüyor.

Filmin ilk öykü sonrasında kameramanın deli danalar gibi Manchaster sokaklarında
yeni bir kahraman aradığı ve boşluğa düşüp bunalıma girdiği sahnesi sinema tarihinin en
kurgusuz ve özgür sahnesi olarak kabul ediliyor. Kameramanın  üzerinden geçen iki katlı
otobüsün kameramanı eziş sesi ise sinema tarihinin en özgün cırk sesi...
Sıradışı yönetmenin bu üçlemesi iki öyküden oluşuyor. Yönetmenin film hakkında yapılan
eleştirilere verdiği ``Ne yani üçleme dedik diye üç film mi çekicez!'' demeci sinema
tarihinin en saçma demeçlerinden.
\end{oz}

\begin{acknowledgments}
I would like to thank everyone. But I am too lazy...
\end{acknowledgments}
\dedication{All carrots I ate}
\tableofcontents
\listoffigures
\listoftables
\begin{glossary}[Symbols]   % default is Abbreviations
\begin{list}{}{\leftmargin=4em\labelwidth=4em\def\makelabel#1{\bf #1 \hfill}}
\item[BB] Bugs Bunny
\item[DD] Duffy Duck
\item[RR] Road Runner
\item[Cyt] Coyote
\item[SC] Silvister the Cat
\item[TwT] Tweety
\item[BB] Bugs Bunny
\item[DD] Duffy Duck
\item[RR] Road Runner
\item[Cyt] Coyote
\item[SC] Silvister the Cat
\item[TwT] Tweety
\item[BB] Bugs Bunny
\item[DD] Duffy Duck
\item[RR] Road Runner
\item[Cyt] Coyote
\item[SC] Silvister the Cat
\item[TwT] Tweety
\item[BB] Bugs Bunny
\item[DD] Duffy Duck
\item[RR] Road Runner
\item[Cyt] Coyote
\item[SC] Silvister the Cat
\item[TwT] Tweety
\item[BB] Bugs Bunny
\item[DD] Duffy Duck
\item[RR] Road Runner
\item[Cyt] Coyote
\item[SC] Silvister the Cat
\item[TwT] Tweety
\end{list}
\end{glossary}
\end{preliminaries}

\input{introduction}
\input{thatsallfolks}
\newpage
\layout

\bibliographystyle{plain}

\nocite{*}
\bibliography{tez-bib}

\begin{vita}
Bugs Bunny was born in 1940 in Brooklyn, New York and the product of many creators: Ben
"Bugs" Hardaway (who created a prototypical version of Bugs Bunny in 1938's Porky's
Hare Hunt), Bob Clampett, Tex Avery, Robert McKimson (created the definitive Bugs Bunny
character design), Chuck Jones, and Friz Freleng. According to Mel Blanc, his original
voice actor, his accent is an equal blend of someone from the Bronx and someone from
Brooklyn. Many children love Bugs Bunny for his funniness and character.

He was nominated 4 times to Academy Award and won once with "Knighty Knight Bugs" in
1958. 
\end{vita}


\end{document}
